Why do people punish? Evidence for a range of strategic concerns

### 2024-01-04 manuscript.tex
update word count
update manuscript

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{punishment; cooperation; economic games\newline\indent Word count: xxxx words}
\usepackage{lineno}

@@

Ethical approval was granted by the University College London Ethics Board
(project: 3720/002). The study was performed in accordance with all the relevant
guidelines and regulations. Informed consent was obtained from all participants
prior to the study and participation was voluntary.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{punishment; cooperation; economic games\newline\indent Word count: 5657 words}
\usepackage{lineno}

@@

This research has been approved by the UCL Department of Psychology Ethics
Committee (project: 3720/002) and ratified by the University of Auckland Human
Participants Ethics Committee. The study was performed in accordance with all
the relevant guidelines and regulations. Informed consent was obtained from all
participants prior to the study and participation was voluntary.
